Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-29 paper/main.tex
color coded intro category things

\begin{definition} A category $\mathcal{C}$ consists of a collection of objects $c$ with identity $id_c: C\rightarrow C$ and the set of morphisms between every two objects $f:C_1 \rightarrow C_2$, \cite{fongInvitationAppliedCategory2019,maclaneCategoriesWorkingMathematician2013}. 
\end{definition}
The set of morphisms between objects is termed the hom set $hom_{\mathcal{C}}(C_1, C_2)$. The morphisms on the category  compose
\begin{equation*}
  \begin{tikzcd}
    C_1 \arrow[r, "f"] \arrow[rd, "g\circ f"'] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145] & C_2 \arrow[d, "g"] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55] \\
  & C_3 \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235]              
  \end{tikzcd}
\end{equation*}
 and are constructed such that the following axioms hold \cite{riehlCategoryTheoryContext}:
 \begin{LaTeXdescription}
   \item[associativity] if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
   \item[identity] for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
 \end{LaTeXdescription}

@@

 \begin{definition} A functor is a morphism between objects of any two  categories $\bm{F}: \mathcal{C} \rightarrow \mathcal{D}$. A functor has the properties of identity and composition \cite{riehlCategoryTheoryContext}\end{definition}

A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. For example, the functor $F:\mathcal{C} \rightarrow \mathcal{D}$ maps an object in $\mathcal{C}$ into an object in $\mathcal{D}$
\begin{equation}
\label{eq:related-work:equivariance:functor_diagram}
\begin{tikzcd}
  c \in Ob(\mathcal{C}) \arrow[d, "f"', shift right=8] \arrow[r, "F"] & F(c) \in Ob(\mathcal{D}) \arrow[d, "F(f)", shift right=8] \\
  c^{\prime} \in Ob(\mathcal{C}) \arrow[r, "F"']                       & F(c^{\prime}) \in Ob(\mathcal{D})                        
  \end{tikzcd}
\end{equation}
 such that for every morphism $f: c \rightarrow c^{\prime} \in Hom(\mathcal{C})$ there is a compatible morphism $F(f): F(c) \rightarrow F(c^{\prime}) \in Hom(\mathcal{D})$. Functors $\bm{F}: \mathcal{C}^{op} \rightarrow \mathcal{D}$ are called contravariant functors.

@@

 \begin{definition} A natural transformation is a morphism of functors $\alpha: F \rightarrow G$ where $F, G$ are functors from $\mathcal{C}$ to $\mathcal{D}$. \cite{riehlCategoryTheoryContext, bradleyWhatNaturalTransformation}
 \end{definition}

\begin{equation}
  \label{eq:related-work:equivariance:natural-transform}
\begin{tikzcd}
  & {} \arrow[dd, "\alpha", Rightarrow, shorten=1.5em] &             \\
\mathcal{C} \arrow[rr, "F", bend left] \arrow[rr, "G"', bend right] &                                     & \mathcal{D} \\
  & {}                                  &            
\end{tikzcd}
\end{equation}
The natural transformation composes with a functor such that the output is a compatible functor between the same categories. This means that for every morphism $f: c \rightarrow c^{\prime}$ between objects in $\mathcal{C}$, there is a commutating naturality square for the corresponding objects in $\mathcal{D}$ \cite{milewskiCategoryTheoryProgrammers}. 
\begin{equation}
  \label{eq:related-work:equivariance:natural_transform_commute}
  \begin{tikzcd}
    c \arrow[rr, "F"] \arrow[rrrr, "G", bend left] \arrow[dd, "f"'] &  & F(c) \arrow[dd, "F(f)"'] \arrow[rr, "\alpha_{c}"] &  & G(c) \arrow[dd, "G(f)"] \\
                                                                    &  & {} \arrow[rr, "\alpha" description, dashed]       &  & {}                      \\
    c^{\prime} \arrow[rr, "F"] \arrow[rrrr, "G", bend right]        &  & F(c^{\prime}) \arrow[rr, "\alpha_{c^{\prime}}"]   &  & G(c^{\prime})          
    \end{tikzcd}
\end{equation}
\note{unpack this a drop more}

>>>>

\begin{definition} A \textcolor{source}{category} $\textcolor{source}{\mathcal{C}}$ consists of a collection of objects $c$ with identity $id_c: C\rightarrow C$ and the set of morphisms between every two objects $f:C_1 \rightarrow C_2$, \cite{fongInvitationAppliedCategory2019,maclaneCategoriesWorkingMathematician2013}. 
\end{definition}
The set of morphisms between objects is termed the hom set $hom_{\mathcal{C}}(C_1, C_2)$. The morphisms on the category  compose
\begin{equation*}
  \begin{tikzcd}
    \textcolor{source}{C_1} \arrow[r, "f", color=source] \arrow[rd, "g\circ f"', color=source] \arrow["id_{C_1}"', loop, distance=2em, in=215, out=145, color=source] & \textcolor{source}{C_2} \arrow[d, "g", color=source] \arrow["id_{C_2}"', loop, distance=2em, in=125, out=55, color=source] \\
  & \textcolor{source}{C_3} \arrow["id_{C_3}"', loop, distance=2em, in=305, out=235, color=source]              
  \end{tikzcd}
\end{equation*}
 and are constructed such that the following axioms hold \cite{riehlCategoryTheoryContext}:
 \begin{LaTeXdescription}
   \item[associativity] if $f: C_1 \rightarrow C_2$, $g: C_2 \rightarrow C_3$ and $h: C_3 \rightarrow C_4$ then $h\circ (g \circ f) = (h \circ g) \circ f$
   \item[identity] for every $f: C_1 \rightarrow C_2$ there exists identity morphisms $f \circ id_{C_1} = f = id_{C_2} \circ f$
 \end{LaTeXdescription}

@@

 \begin{definition} A functor is a morphism between objects of any two  categories $\textcolor{sheaf}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$. A functor has the properties of identity and composition \cite{riehlCategoryTheoryContext}\end{definition}

A functor preserves the structure of the category, namely morphisms and the source and target objects of those morphisms, composition of morphisms, and identity morphisms \cite{riehlCategoryTheoryContext}. For example, the functor $\textcolor{functor}{F}:\mathcal{C} \textcolor{functor}{\rightarrow} \mathcal{D}$ maps an object in $\textcolor{source}{\mathcal{C}}$ into an object in $\textcolor{target}{\mathcal{D}}$
\begin{equation}
\label{eq:related-work:equivariance:functor_diagram}
\begin{tikzcd}
  \textcolor{source}{c} \arrow[d, "f"', shift right=0, color=source] \arrow[r, "F", color=functor] & \textcolor{target}{F(c)} \arrow[d, "F(f)", shift right=0, color=target] \\
  \textcolor{source}{c^{\prime}} \arrow[r, "F"', color=functor]                       & \textcolor{target}{F(c^{\prime})}                      
  \end{tikzcd}
\end{equation}
 such that for every morphism $f: c \rightarrow c^{\prime} \in Hom(\mathcal{C})$ there is a compatible morphism $F(f): F(c) \rightarrow F(c^{\prime}) \in Hom(\mathcal{D})$. Functors $\bm{F}: \mathcal{C}^{op} \rightarrow \mathcal{D}$ are called contravariant functors.

@@

 \begin{definition} A \textcolor{nattran}{natural transformation} is a morphism of functors $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$ where $F, G$ are functors from $\mathcal{C}$ to $\mathcal{D}$. \cite{riehlCategoryTheoryContext, bradleyWhatNaturalTransformation}
 \end{definition}

\begin{equation}
  \label{eq:related-work:equivariance:natural-transform}
\begin{tikzcd}
  & {} \arrow[dd, "\alpha", Rightarrow, shorten=1.5em, color=nattran] &             \\
\textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor] \arrow[rr, "G"', bend right, color=functor] &                                     & \textcolor{target}{\mathcal{D}} \\
  & {}                                  &            
\end{tikzcd}
\end{equation}
The natural transformation composes with a functor such that the output is a compatible functor between the same categories. This means that for every morphism $f: c \rightarrow c^{\prime}$ between objects in $\mathcal{C}$, there is a commutating naturality square for the corresponding objects in $\mathcal{D}$ \cite{milewskiCategoryTheoryProgrammers}. 
\begin{equation}
  \label{eq:related-work:equivariance:natural_transform_commute}
  \begin{tikzcd}
    \textcolor{source}{c} \arrow[rr, "F", color=functor, alpha=.5] \arrow[rrrr, "G", bend left, color=functor, alpha=.5] \arrow[dd, "f"', color=source] &  & \textcolor{target}{F(c)} \arrow[dd, "F(f)"', color=target] \arrow[rr, "\alpha_{c}", color=artist] &  & \textcolor{target}{G(c)}\arrow[dd, "G(f)", color=target] \\
                                                                    &  & {} \arrow[rr, "\alpha" description, dashed, color=artist]       &  & {}                      \\
    \textcolor{source}{c^{\prime}} \arrow[rr, "F", color=functor, alpha=.5] \arrow[rrrr, "G", bend right, color=functor, alpha=.5]        &  & \textcolor{target}{F(c^{\prime})} \arrow[rr, "\alpha_{c^{\prime}}", color=artist]   &  & \textcolor{target}{G(c^{\prime})}          
    \end{tikzcd}
\end{equation}
\note{unpack this a drop more}
